---
title: "Classwork 6.2"
output: html_notebook
---

# Downloading and Installing Packages
You only have to do this once. If you did it last time (and you are using the same computer), you don't need to run it this time.

```{r}
# install multiple packages at once
install.packages(pkgs = c("dplyr", "ggplot2", "ggformula",
"mosaic", "supernova", "lsr","Lock5Data", "Lock5withR",
"okcupiddata", "dslabs","fivethirtyeight"))
```


# Loading Packages
You have to run these for every notebook or every session of R. You have the libraries but you need to tell R that you want to use them right now.

```{r}
library(dplyr)
library(ggplot2)
library(ggformula)
library(mosaic)
library(supernova)
library(lsr)
library(Lock5withR)
library(okcupiddata)
library(dslabs)
library(fivethirtyeight)
```

# Questions from PollEverywhere

These were questions asked via PollEverywhere. I tried to answer the questions using these examples.

*Question(s):* Will we be tested on vline? And hline? When would we use vline and hline?

*Answer:* For now, you might need vline or hline so that you can see where the mean and/or median might be relative to some visualization. For example, you might want to put the mean as a line on a histogram or a boxplot.

```{r}
# pulling in the PRAISESTUDY data from the internet
PRAISESTUDY <- read.csv("http://bit.ly/muellerdweck_study1", header=TRUE)
```

```{r}
# helps to save the favstats so you can use them repeatedly
PS3.stats <- favstats(~ PS3, data = PRAISESTUDY)
PS3.stats

# here's how to use vline with a histogram
gf_histogram(~ PS3, data = PRAISESTUDY, fill="magenta", color = "darkgray", binwidth = 1) %>%
gf_facet_grid(FEEDBACK ~ .) %>%
gf_vline(xintercept = ~mean, data = PS3.stats)
```

```{r}
# here is an example of hline
gf_boxplot(PS3 ~ FEEDBACK, data = PRAISESTUDY, color = "magenta") %>%
gf_hline(yintercept = ~mean, data = PS3.stats)
```

*Question:* making new variables using $ and then using them in functions. Another person asked: For residuals all we have to do is put resid(Empty.model)

*Answer:*

```{r}

```

gf_histogram(~ Points, data = MiamiHeat, color = "tomato3") %>%
gf_facet_grid(Win ~ .)

HeatWin <- filter(MiamiHeat, Win == "W")
gf_histogram(~ Points, data = HeatWin, color = "tomato3")

empty.model <- lm(Points ~ NULL, data = MiamiHeat)
MiamiHeat$residual <- resid(empty.model)

head(MiamiHeat)

sum(MiamiHeat$residual)
sum(~ residual, data = MiamiHeat)
mean(MiamiHeat$residual)
mean(~ residual, data = MiamiHeat)


MiamiHeat$FG.shuff <- shuffle(MiamiHeat$FG)
head(select(MiamiHeat, Points, FG, FG.shuff))

gf_point(Points ~ FG.shuff, data = MiamiHeat, size = 4, color = "black")

gf_point(Points ~ shuffle(FG), data = MiamiHeat, size = 4, color = "darkgray")
```

# Sum of Squares with R

Different ways of calculating sum of squares in R. Here are three ways of finding sum of squares (for Points) in R.

## Using anova() 
```{r}
empty.model <- lm(Points ~ NULL, data = MiamiHeat)
anova(empty.model)
```

## Find at least one other way of calculating Sum of Squres

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.



# Pros and Cons of SS

What is good about SS?

What’s the problem with SS? (That is, why do we need Variance and Standard Deviation?)

```{r}
# Make a faceted histogram of Points by Win (winning games vs. losing games)

```

Which distribution (W or L) looks like it would have more error around it's mean?

Which distribution will have a much bigger SS?

Which distribution will have a much bigger variance or standard deviation?

# Seeing Standard Deviation

```{r}
# Make a histogram of Points and put in a line for the mean

```

Points: Where is the standard deviation on this histogram? (gesture)
If you aren't sure, ask yourself where are the residuals? SS? Variance? StDev? (gesture)

```{r}
# Find the standard deviation of Points

```

Come up with a strategy to try to "see" the standard deviation in the histogram of Points.

Test your strategy: Estimate the Standard Deviation of Assists
```{r}
# Make a histogram of Assists and estimate the standard deviation

```

Your estimate: 

```{r}
# Calculate the standard deviation of Assists

```

Test your strategy: Estimate the Standard Deviation of FG3
```{r}
# Make a histogram of FG3 and estimate the standard deviation

```

Your estimate: 

```{r}
# Calculate the standard deviation of FG3

```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
