---
title: "Classwork 7.2"
output:
  html_document:
    df_print: paged
---

# Loading Packages
You have to run these for every notebook or every session of R. You have the libraries but you need to tell R that you want to use them right now.

```{r, include = FALSE}
# the include = FALSE part gets rid of all that junk that gets printed out from loading the libraries

library(dplyr)
library(ggplot2)
library(ggformula)
library(mosaic)
library(supernova)
library(lsr)
library(Lock5withR)
library(okcupiddata)
library(dslabs)
library(fivethirtyeight)
```

# Classwork 7.2 

```{r preparedata}
library(fivethirtyeight)
drinks$Country <- drinks$country
happydrinks <- left_join(HappyPlanetIndex, drinks, by = "Country")
```

Look through the variables in happydrinks and come up with a DGP for happiness. What explains the variation we see in happiness around the world? 

Word equation:

Explanation:

Explore your idea of the DGP with a visualization here.
```{r}

```

Put the empty model on your visualization.
```{r}

```

Do you think the variation is better explained by randomness (i.e., the empty model) or by your explanation? 

What features of the visualization make you think that one explanation is better than the other?